### 2021-03-03 Manuscript/manuscript.tex
PUB

know as the basic reproduction factor. This number, that is the average number of people that are infected by a single individual, describe if the epidemic is in a negative feedback (R$_{0}$<1), stationary (R$_{0}$=1), or in a positive feedback (R$_{0}$>1). As consequence if the epidemic is in a negative feedback it will be going to dissipate, if it is in positive feedback it will grow. Note that in this simple model since the parameters are not time dependent this factor is constant. If, as performed by Ferrari et al. \cite{ferrari2020modelling}, time dependent parameters are considered a time depended parameter called $R_{t}$. For the present work, we limited to constant parameters: in particular we considered the parameter estimation for Lombardy provided by Neves and Guerrero in Ref \cite{neves2020predicting}: $\beta$ was set equal to 0.55 while $\gamma$ equal to $\frac{1}{7}$. The overall population $N$ was set to 60M, in order to simulate Italian population.  Within the daily temporal evolution of this model, that was obtained by numerically solving the differential equation above via the \textit{DeSolve} package, we considered a trigger activated by the PM every 7 days: if the number of infected people normalized by the overall population is more than $1\times 10^{-7}$, there is a probability that the PM impose laws that multiply the $\beta$ factor by $0.7$, if the normalized infected people are more than 10 the previous threshold  she will impose, with a certain probability, restrictions that multiply the $\beta$ starting $\beta$ factor by $0.25$, finally if the  threshold is exceeded more than 50 times the PM will impose with a certain probability restrictive measures that multiply the $\beta$ by $0.025$. These attenuation parameters were adjusted taking in consideration the results of Marziano et al. in Ref. \cite{marziano2021retrospective}. As we said the PM act with a certain probability, more formally stochastically: each week a random number is extracted, if this is higher than a certain threshold the relative restrictive decision is taken, otherwise not. The threshold value capture the PM attitude to impose the lock-down: lower values model a careful PM, hight value a lazy one. In this way the model is able to simulate different scenarios for the different PM attitude: as we will see this can produce two very different results. At the end of the simulation, beside the values given by the standard SIRD model (recovered and deaths), the model also provide the number of days in which each restriction was active: these values are then used for the economic model in order to evaluate the economic effect due to the restrictions.

@@

The values obtained previous are used in the following way to evaluate the economic impact: the number of deaths is multiplied by the maximum compensation value provided by the Court of Milan \cite{tribunaleMilano} for manslaughter (300K EUR), this choice is based on the idea that, the PM, if act improperly, can be incriminated for manslaughter and than, if judged guilty,  charged by this amount for each death\footnote{In principle the judge also keep into account the age of the deaths: this in principle require a model in which also the age of people is keep into account. In this case however a system of partial differential equation should be solved making the calculation and the computational cost incredibly high.}. Beside this impact there is also the cost associated to the medical care of each ill people, for this we considered the average value calculated by National Anti-Corruption Authority (ANAC) \cite{Anac}: 28.180 kEUR.

>>>>

know as the basic reproduction factor. This number, that is the average number of people that are infected by a single individual, describe if the epidemic is in a negative feedback (R$_{0}$<1), stationary (R$_{0}$=1), or in a positive feedback (R$_{0}$>1). As consequence if the epidemic is in a negative feedback it will be going to dissipate, if it is in positive feedback it will grow. Note that in this simple model since the parameters are not time dependent this factor is constant. If, as performed by Ferrari et al. \cite{ferrari2020modelling}, time dependent parameters are considered a time depended parameter called $R_{t}$. For the present work, we limited to constant parameters: in particular we considered the parameter estimation for Lombardy provided by Neves and Guerrero in Ref \cite{neves2020predicting}: $\beta$ was set equal to 0.55 while $\gamma$ equal to $\frac{1}{7}$. The overall population $N$ was set to 60M, in order to simulate Italian population.  Within the daily temporal evolution of this model, that was obtained by numerically solving the differential equation above via the \textit{DeSolve} package, we considered a trigger activated by the PM every 7 days: if the number of infected people normalized by the overall population is more than $1\times 10^{-7}$, there is a probability that the PM impose laws that multiply the $\beta$ factor by $0.7$, if the normalized infected people are more than 10 the previous threshold  she will impose, with a certain probability, restrictions that multiply the $\beta$ starting $\beta$ factor by $0.25$, finally if the  threshold is exceeded more than 50 times the PM will impose with a certain probability restrictive measures that multiply the $\beta$ by $0.025$. These attenuation parameters were adjusted taking in consideration the results of Marziano et al. in Ref. \cite{marziano2021retrospective}. As we said the PM act with a certain probability, more formally stochastically: each week a random number (from zero to one) is extracted, if this is higher than a certain threshold, the relative restrictive decision is taken, otherwise not. The threshold value capture the PM attitude to impose the lock-down: lower values model a careful PM, hight value a lazy one. In this way the model is able to simulate different scenarios for the different PM attitude: as we will see this can produce two very different results. At the end of the simulation, beside the values given by the standard SIRD model (recovered and deaths), the model also provide the number of days in which each restriction was active: these values are then used for the economic model in order to evaluate the economic effect due to the restrictions and PM strategy.

@@

The economic impact for each epidemiological scenario is shaped as follow: the number of deaths is multiplied by the maximum compensation value provided by the Court of Milan \cite{tribunaleMilano} for manslaughter (300k EUR). This choice is based on the idea that, if the PM act improperly, can be incriminated for manslaughter and than, if judged guilty,  charged by this amount for each death\footnote{In principle the judge also keep into account the age of the deaths: this in principle require a model in which also the age of people is keep into account. In this case however a system of partial differential equation should be solved making the calculation and the computational cost incredibly high.}. Beside this impact there is also the cost associated to the medical care of each ill people, for this we considered the average value calculated by National Anti-Corruption Authority (ANAC) \cite{Anac}: 28.180 kEUR \footnote{It is worth noting that, in principle, there is also another import health-care impact due to the fact that the ill people for COVID-19 saturate the health system thus making it unreachable for other disease. This spillover translates in to more death and more ill people with respect to the baseline situation where there isn't an pandemic: however, by now, this effect is difficult to quantify and so we did not included in to the present model}.

### 2021-03-03 Presentazione/Presentation.tex
PUB

\useoutertheme{miniframes}

@@

\begin{frame}
\frametitle{Regression}
\begin{itemize}
\item T Variabile temporale: n numero di mesi prima di Febbraio (ultimo mese senza lock-down)
\item $T1$,$T2$ e $T3$ dummy per i 3 livelli di lockdown: T1 per Marzo e Maggio (MEDIUM), T2 Aprile (HIGH) e T3 Giugno (LOW). Nei grafici questo periodo è segnato dalle barre tratteggiate.
\item $Y_{x}$ volume di vendite per il settore x 
\end{itemize}
\begin{equation}
Y_{x}-Y_{Alimentare}=\alpha+\delta_{before T1}T+\delta_{T1}T_{1}+\delta_{T2}T_{2}+\delta_{T3}T_{3}+\epsilon
\end{equation}
\end{frame}

@@

%\subsection{Stars Feature}

%\begin{frame}
%\frametitle{Theoretical background - Star features }
%\begin{columns}
%\column{0.4\textwidth}
%\begin{itemize}
%\item \textbf{Main features}: For this work the main features of star are the stellar luminosity (S\_L), its temperature (S\_T) and spectral type (S\_S\_T)
%\item\textbf{H-R diagram}: with these features the Hertzsprung-Russell diagram classify the stars (the temperature and spectral type of a star are two faces of the same medal)
%\end{itemize}
%\column{0.45\textwidth}
%\includegraphics[width=\linewidth,]{Pic/S_T_T_explanation.png}
%\begin{center}
%Image taken from \cite{HR_diagram}
%\end{center}
%\end{columns}
%\end{frame}

>>>>

\useoutertheme{miniframes}
\DeclareUnicodeCharacter{200A}{!!!FIX ME!!!}

@@

\begin{frame}
\frametitle{Trend Check}
\begin{itemize}
\item T Variabile temporale: n numero di mesi prima di Febbraio (ultimo mese senza lock-down)
\item $T1$,$T2$ e $T3$ dummy per i 3 livelli di lockdown: T1 per Marzo e Maggio (MEDIUM), T2 Aprile (HIGH) e T3 Giugno (LOW). Nei grafici questo periodo è segnato dalle barre tratteggiate.
\item $Y_{x}$ volume di vendite per il settore x 
\item I dati sono stati raccolti dal sito ISTAT 
\end{itemize}
\begin{equation}
Y_{x}-Y_{Alimentare}=\alpha+\delta_{before T1}T+\delta_{T1}T_{1}+\delta_{T2}T_{2}+\delta_{T3}T_{3}+\epsilon
\end{equation}
\end{frame}

@@

\begin{frame}
\frametitle{DID estimation with deseasonalized data}
\begin{itemize}
\item C dummy per il gruppo di controllo (Alimentari), $T1$,$T2$ e $T3$ dummy per i 3 livelli di lockdown: T1 per Marzo e Maggio (MEDIUM), T2 Aprile (HIGH) e T3 Giugno (LOW)
\item DID a più tempi come già sviluppato con successo da Draca et. al in \cite{draca2011panic} and da Wooldridge in  \cite{wooldridge2012introductory}

\end{itemize}
\begin{equation*}
Y=C+T_{1}+T_{2}+T_{3}+\delta_{1}(T_{1}\times C)+\delta_{2}(T_{2}\times C)+\delta_{3}(T_{3}\times C)+\epsilon
\end{equation*}
\begin{table}[]
\begin{tabular}{l|l|l|l|l|l|l|l|l|l|l|l|l}
                 & $\delta_{1}$     & $\sigma_{\delta_{1}} $   & $\delta_{2}  $    &$ \sigma_{\delta_{2}}  $   & $\delta_{3}     $ & $\sigma_{\delta_{3}} $    \\ \hline
Abbigliamento    & -40.16 & 2.01 & -60.07 & 2.77 & -16.46 & 2.77  \\ \hline
Calzature        & -38.70 & 1.73 & -65.78 & 2.39 & -20.62 & 2.39  \\ \hline
Elettrodomestici & -20.32 & 2.5  & -27.34 & 3.45 & -3.68  & 3.45  \\ \hline
Fotoottica       & -34.14 & 2.55 & -52.32 & 3.52 & -7.8   & 3.52 \\ \cline{1-1}
\end{tabular}
\end{table}
\end{frame}

\begin{frame}
\frametitle{DID estimation with RAW data}
\begin{itemize}
\item C dummy per il gruppo di controllo (Alimentari), $T1$,$T2$ e $T3$ dummy per i 3 livelli di lockdown: T1 per Marzo e Maggio (MEDIUM), T2 Aprile (HIGH) e T3 Giugno (LOW)
\item Errore decisamente maggiore rispetto ai dati de-stagionalizzati
\end{itemize}
\begin{equation*}
Y=C+T_{1}+T_{2}+T_{3}+\delta_{1}(T_{1}\times C)+\delta_{2}(T_{2}\times C)+\delta_{3}(T_{3}\times C)+\epsilon
\end{equation*}
\begin{table}[]
\begin{tabular}{l|l|l|l|l|l|l|l|l|l|l|l|l}
                 & $\delta_{1}$     & $\sigma_{\delta_{1}} $   & $\delta_{2}  $    &$ \sigma_{\delta_{2}}  $   & $\delta_{3}     $ & $\sigma_{\delta_{3}} $    \\ \hline
Abbigliamento    & -60.70 & 13.32 & -90.89 & 13.32 & -15.69 & 13.32  \\ \hline
Calzature        & -57.37 & 14.95 & -95.97 & 20.76 & -11.70 & 8.67  \\ \hline
Elettrodomestici & -41.81 & 16.47  & -68.26 & 22.88 & 3.24  & 9.56  \\ \hline
Fotoottica       & -45.33 & 9.22 & -76.48 & 12.80 & -3.77   & 5.35 \\ \cline{1-1}
\end{tabular}
\end{table}
\end{frame}

\begin{frame}
\frametitle{DID estimation - placebo (deseasonalized data)}
\begin{table}[]
\begin{tabular}{l|l|l|l|l|l|l|l|l|l|l|l|l}
                 & $\delta_{4}$     & $\sigma_{\delta_{4}} $   & $\delta_{5}  $    &$ \sigma_{\delta_{5}}  $   & $\delta_{6}     $ & $\sigma_{\delta_{6}} $    \\ \hline
Abbigliamento     & 3.94 & 12.65 & 4.87 & 17.47 & 0.70  & 17.47 \\ \hline
Calzature        & 5.04 & 13.14 & 5.31 & 18.15 & 2.00  & 18.16 \\ \hline
Elettrodomestici   & 1.13 & 6.26  & 4.63 & 8.65  & -0.81 & 8.65  \\ \hline
Fotoottica        & 0.84 & 10.98 & 1.71 & 15.18 & 0.69  & 15.18 \\ \cline{1-1}
\end{tabular}
\end{table}
\end{frame}

\begin{frame}
\frametitle{DID - Cassa integrazione}
\centering
\includegraphics[width=10cm,height=7cm]{Pic/CIG_TOT.pdf}\\

\end{frame}

\begin{frame}
\frametitle{DID - Cassa integrazione}
\begin{columns}[t]
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{Pic/Manifattura_CIG.pdf}\\
\includegraphics[width=5cm,height=3.5cm]{Pic/Commercio_CIG.pdf}
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{Pic/Costruzioni_CIG.pdf}\\
\includegraphics[width=5cm,height=3.5cm]{Pic/Immob_CIG.pdf}
\end{columns}
\end{frame}

\begin{frame}
\frametitle{References}
\printbibliography
\end{frame}
